Sequential rank agreement methods for comparison of ranked lists

### 2015-05-23 latex/paper.Rnw
Style

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{calc}
\usepackage[noae]{Sweave}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{algpseudocode}
%
% New commands
%
\newcommand{\ie}{\emph{i.e.}\@\xspace}
\newcommand{\eg}{\emph{e.g.}\@\xspace}

@@

\begin{algorithm}
\caption{Sequential rank agreement algorithm for censored lists}
\label{sra-algorithm}
\begin{algorithmic}[1]
\Procedure{Censored rank agreement}{}
\State Let $B$ be the number of permutations to use
\For{each $b \in B$}
\For{each censored list $l \in L$}
\State \parbox[t]{\dimexpr\linewidth-\algorithmicindent-2cm}{Permute the unassigned ranks, $k_l+1, \ldots, P$ and assign
them randomly to the items \emph{not} found in the list, i.e.,
$\Lambda^\complement$, in order to fill out the lists.}
\EndFor
\State \parbox[t]{\dimexpr\linewidth-\algorithmicindent-1cm}{Let sra($b$) be the sequential rank agreement computed from the
filled out lists.}
\EndFor
\State Return element-wise averages across all $B$ permutations of sra($b$).
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\bibliographystyle{apalike}
\bibliography{paperref}

>>>>

\documentclass[12pt,a4paper]{statsoc}
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{calc}
\usepackage[noae]{Sweave}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{algpseudocode}
%
% New commands
%
\newcommand{\ie}{\emph{i.e.}\@\xspace}
\newcommand{\eg}{\emph{e.g.}\@\xspace}

@@

\begin{algorithm}
\caption{Sequential rank agreement algorithm for censored lists}
\label{sra-algorithm}
\begin{algorithmic}[1]
\Procedure{Censored rank agreement}{}
\State Let $B$ be the number of permutations to use
\For{each $b \in B$}
\For{each censored list $l \in L$}
\State \parbox[t]{\dimexpr\linewidth-\algorithmicindent-1.7cm}{Permute the unassigned ranks, $k_l+1, \ldots, P$ and assign
them randomly to the items \emph{not} found in the list, i.e.,
$\Lambda^\complement$, in order to fill out the lists.}
\EndFor
\State \parbox[t]{\dimexpr\linewidth-\algorithmicindent-1cm}{Let sra($b$) be the sequential rank agreement computed from the
filled out lists.}
\EndFor
\State Return element-wise averages across all $B$ permutations of sra($b$).
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\bibliographystyle{rss}
\bibliography{paperref}
